Visualizations for the manuscript

### 2022-02-27 metanalysis_visualization/manuscript_Figures.Rmd
CCHMC added
add APHP and CCHMC to the visualization notebook

df_coefficients_boot <- bootstrapped_coefficients_all %>% 
  left_join(coefficients_df, by = "siteid") %>% 
  filter(siteid != "APHP")

@@

positions <- c("BCH", "CHOP", "UMICH", "Lurie", "FRBDX")

>>>>

df_coefficients_boot <- bootstrapped_coefficients_all %>% 
  left_join(coefficients_df, by = "siteid")

@@

positions <- c("BCH", "CCHMC","CHOP", "UMICH", "Lurie", "FRBDX", "APHP")
